%add acknowledgements here

I would like to thank many people for helping me to complete this research. First, I must
thank my survey interview participants for their involvement, as well as all of the participants
across the many secondary data sources I used. 

I have to thank my instructors and mentors who have helped me become a better researcher, 
sociologist, and social data scientist. From Trinity College, Dublin, the University of Arizona, 
to my work in industry, I have had strong mentors who challenged me to continually
dive a little deeper and make sure my findings were rigorous and robust 
to study the social world in a systemic manner. 
My dissertation chair and committee, in particular, deserve all my gratitude for their caring guidance and feedback on these three articles. 

A major thank you to my other half who has been there every step of the way, from every late-night walk, 
surprise doughnut, or last minute proofreading. You were there with me for every moment of
self-doubt to immense celebration and never ceased to cheer me on. 
I couldn't have done this without you.

Finally, thank you to all others who have believed in my work and supported me along the way. 
To those who have provided funding through fellowships and grants, 
like the Louise Foucar Marshall Foundation,
the UArizona Hispanic Alumni Club, 
the UArizona Social \& Behavioral Sciences Research Institute,
The UArizona Data Science Institute, 
the American Sociological Association Student Forum and
the Summer Institute in Computational Social Science: thank you.
To my fellow classmates, friends, and 
collaborators throughout my academic journey, you inspired me and made my work better! 

% Spouse, Family, Coco

% % Fellowships: 
% UArizona Social \& Behavioral Sciences Graduate Fellowship
% Louise Foucar Marshall Foundation
% UArizona Diversity and Inclusion Fellowship
% University of Arizona Hispanic Alumni Club Graduate Scholarship 

% % Funding:
% Russel Sage Foundation - Summer Institute in Computational Social Science Research Grant
% UArizona SBSRI Dissertation Research Grant 
% American Sociological Association Student Forum Travel Award to present my research...

% % mentors
% Ronald Breiger
% Daniel E. Martinez
% Corey Abramson
% Terrence Hill (maybe demote to various other collaborators)
% Yotam Shmargad

%  Javier Osorio
%  Robin Stryker, Bethany A. Conway-Silva
%  Albert Bergesen

% Jeff Oliver, Adriana Picoral

% Daniel Faas
% David Landy	
% Richard Layte	

% Thomas Davidson

% % from the department
% meltem, darla, Amelia Blume, morgan
% rina
% eric
% beksahn, liwen
% eunsung, jina, peter, yiru, minyoung

% % out of the department and various other collaborators
% karen de la rosa
% laura wethmann dozal 
% victoria money
% Alejandro Beltran
% Adriana Picoral
% nicolas legewie

%  Sara Singleton
%  Ciaran Devlin
 
%  Munir Al Akari
%  Bashayer Al-Ali
%  Gareth Aled Davies

% communities.. 
% data science institute, 
% resbaz
% TechnoSoc
% WiDS Tucson
% The Carpentries, RStudio
% Mathematical Sociology Section

% To the communities within my department, 
% communities.. 
% data science institute, 
% resbaz
% TechnoSoc
% WiDS Tucson
% The Carpentries, RStudio
% Mathematical Sociology Section